Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Remove redundant OSM shortening references

A possible way of mitigating this problem is looking towards gathering geodata from volunteer-based geoservices such as OpenStreetMap (OSM), where the temporal aspect of data accuracy is perhaps more assured by the crowd contribution nature.
There are already a few such services that use OSM data to generate 3D geodata visualizations for data visualization and video game applications.
A few prominent examples are Mantle
\footnote{Mantle homepage. Accessed 17-05-2020. https://www.mantle.tech/}
and Mapbox
\footnote{Mapbox homepage. Accessed 17-05-2020. https://www.mapbox.com/}.
Such services are however usually limited in the accuracy and type of data that they can provide.
While they can provide both builing footprints and road networks, they usually provide road data with no respect to overlap between features.
Collision between road meshes in 3D will lead to strange-looking mesh intersections and inaccuracies that modelers often want to avoid.
In particular, streets and roads designated for energy efficient mobility, such as footpaths, are much more organic and dense in their nature than main streets, and thus the risk of feature collision may be higher.

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OpenStreetMap (OSM) data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (***find reference)

>>>>

A possible way of mitigating this problem is looking towards gathering geodata from volunteer-based geoservices such as OSM, where the temporal aspect of data accuracy is perhaps more assured by the crowd contribution nature.
There are already a few such services that use OSM data to generate 3D geodata visualizations for data visualization and video game applications.
A few prominent examples are Mantle
\footnote{Mantle homepage. Accessed 17-05-2020. https://www.mantle.tech/}
and Mapbox
\footnote{Mapbox homepage. Accessed 17-05-2020. https://www.mapbox.com/}.
Such services are however usually limited in the accuracy and type of data that they can provide.
While they can provide both builing footprints and road networks, they usually provide road data with no respect to overlap between features.
Collision between road meshes in 3D will lead to strange-looking mesh intersections and inaccuracies that modelers often want to avoid.
In particular, streets and roads designated for energy efficient mobility, such as footpaths, are much more organic and dense in their nature than main streets, and thus the risk of feature collision may be higher.

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OSM data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (***find reference)
